---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# farbteiler

<!-- badges: start -->
![example workflow](https://github.com/mlhollestelle/farbteiler/actions/workflows/r.yml/badge.svg)
<!-- badges: end -->

An R-package to generate art inspired by [farbteiler](https://erikswahn.com/farbteiler/) by Erik Swahn. Erik Swahn is the creator behind the system and this is just a mere implementation of his idea based on available documentation of the system. This library is for personal use only.

## Installation

You can install the released version of farbteiler from github:

``` r
remotes::install_github("mlhollestelle/farbteiler")
```
## Usage

Use the function `farbteiler()` to plot the object.

```{r example}
library(farbteiler)
farbteiler()
farbteiler()
farbteiler()
farbteiler()
farbteiler()
farbteiler()
```
